Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd
sldies

-   Quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different tournament structures recover the true ranking of the teams

>>>>

-   Quantify how well a structure can accurately order the competitors using weighted mutual information
-   We propose a metric that quantifies how effectively different tournament structures recover the true ranking of the teams
